### 2022-11-25 manuscript.Rmd
Fix ggplot syntax in other plot too

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            size = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B1 \n') +
  scale_color_discrete('inter-factor \ncovariance') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

@@

While we demonstrate in this tutorial that simulation-based techniques help overcome methodological shortcomings from traditional analytical approaches, the randomness that is inherent to such approaches may seem at odds with efforts in results reproducibility and replicability. Here, a clear-cut solution is through transparent and accessible documentation of the simulation code and adequate software management. That is, researchers should make use of repositories on platforms such as GitHub or the Open Science Framework to make code scripts available to other researchers, and clearly specify the versions of software programs and packages that were used (e.g. via containerization or at least in written form). We thus urge researchers to seriously consider the issue of reproducibility for their simulation analyses, to make outcomes of such a-priori power estimates easily accessible to other researchers and reviewers [for a more detailed guideline on a reproducible workflow in R see @peikert_2021 and the implementation of this manuscript on GitHub as an example]. Note, however, that (specifically in cases when simulations are parallelized on computing clusters) the exact replicability of simulations as demonstrated in this tutorial might be compromised, even when a seed is specified in the analysis script. Nevertheless, a sufficiently high number of iterations should result in equivalent estimates of statistical power and thus the derived conclusions about required sample size will remain unaffected.

>>>>

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B1 \n') +
  scale_color_discrete('inter-factor \ncovariance') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

@@

While we demonstrate in this tutorial that simulation-based techniques help overcome methodological shortcomings from traditional analytical approaches, the randomness that is inherent to such approaches may seem at odds with efforts in results reproducibility and replicability. Here, a clear-cut solution is through transparent and accessible documentation of the simulation code and adequate software management. That is, researchers should make use of repositories on platforms such as GitHub or the Open Science Framework to make code scripts available to other researchers, and clearly specify the versions of software programs and packages that were used (e.g. via containerization or at least in written form). We thus urge researchers to seriously consider the issue of reproducibility for their simulation analyses, to make outcomes of such a-priori power estimates easily accessible to other researchers and reviewers [for a more detailed guideline on a reproducible workflow in R see @peikert_2021 and the implementation of this manuscript on GitHub as an example]. Note, however, that - specifically in cases when simulations are parallelized on computing clusters - the exact replicability of simulations as demonstrated in this tutorial might be compromised, even when a seed is specified in the analysis script. Nevertheless, a sufficiently high number of iterations should result in equivalent estimates of statistical power and thus the derived conclusions about required sample size will remain unaffected.
